In this section we describe the adversarial model and introduce the stopping condition of \Providence, proving some of its properties.

%Recall that the proof that the \Minerva audit is risk-limiting assumes that the round schedule of \Minerva is predetermined and that, in particular, an adversarial auditor cannot determine the next round size after drawing a sample (we termed such an adversary a weak adversary in section \ref{sec:adv}). This presents difficulties because a non-adversarial election official might want to draw a small next round if the current sample comes close to satisfying the risk limit. Because the \Minerva round size is predetermined, however, the election official would be required to draw a larger round size than necessary for the sample. Conversely, if the current sample is not at all close to satisfying the risk limit, it would be advantageous to draw a larger round than the predetermined round size. Thus it would be advantageous to have an RLA with \Minerva's efficiency advantages in the face of an adversarial auditor who could choose next round sizes after drawing the sample (we termed such an adversary a strong adversary). This would enable honest participants to better plan audits. 

%Before proceeding to define the audit \Providence which is an RLA in the presence of the stronger adversary, we formalize the notions of weak and strong adversaries introduced in section \ref{sec:adv}.

\subsection{Adversarial Model for RLAs}
\label{sec:adv}
Detailed descriptions of best practices for post-election audits may be found in \cite{best-practices,why-and-how}. For our purposes, we will assume that best practices are followed: the paper trail consists of hand-marked paper ballots and is secured; a public compliance audit is carried out before the RLA to ensure that the processes for securing the paper trail were followed; voter authentication and registration processes are verified; and 
%only legitimate voters cast no more than a single vote each; 
the risk-limiting audit is public. We will further assume that all software used in the RLA is open source and well-defined, so its output may be reproduced and thus verified by an observer wishing to do so with their own software. 

Referring to the ballot polling audit steps described in section \ref{sec:polling}, we further assume that the ballot manifest is verified by the compliance audit; a secure PRNG is used; the seed is generated uniformly at random in a public process; the process of locating ballots is publicly observable and the located ballots can be viewed by the public. Because the PRNG is well-defined, as is the stopping condition, we may assume that the stopping condition is correctly computed, because it can be checked by the public through knowledge of the seed and the drawn ballots. Thus the only variable is round size. 

We define a {\em weakly round-choosing adversary} as one who can choose the first and subsequent round sizes before the audit begins and a {\em strongly round-choosing adversary} as one who can choose any round size at any time (before, of course, that particular round begins). In particular, a strongly round-choosing adversary may use information about the sample drawn thus far to decide the next round size, but a weakly round-choosing adversary may not. 

\begin{definition}[Weakly Round-Choosing Adversary]
A {\emph weakly round-choosing adversary} may choose the first and consequent round sizes as a pre-determined function of audit parameters. That is, the $j^{th}$ round size is a function $$n_j(\alpha, p_a, p_0, ballot\_manifest)$$ determined before the audit begins. 
\end{definition}

\begin{definition}[Strongly Round-Choosing Adversary]
A {\emph strongly round-choosing adversary} may choose any round size as any function of audit parameters and all preceding samples. That is, the first round size is a function 
$$n_1(\alpha, p_a, p_0, ballot\_manifest),$$
and for all rounds $j\ge 2$, the round size is a function
$$n_{j}(\alpha, p_a, p_0, ballot\_manifest, \bm{k_{j-1}}, \bm{n_{j-1}})$$ The functions $n_j$, $j \geq 1$ may be chosen at any time before the $j^{th}$ round begins. 
\end{definition}

\subsection{Intuition Behind the Properties of \Providence}
Before defining \Providence, we give some intuition for how it is designed to avoid the problem of \Minerva.

Consider any ballot polling audit in round $j$, designed to stop for some value of $K_j=k_j$ smaller than the round size. In general, if $k_j$ is large, the probability of this value of $K_j$ given a correct outcome, $Pr[K_j = k_j \mid H_1]$, is larger than the corresponding risk---$Pr[K_j = k_j \mid H_0]$, the probability of this value of $K_j$ given a tie. The risk is generally not zero, however. Thus, corresponding to each such value of $K_j$, a risk is incurred. To obtain the total risk for the round, one adds the risks corresponding to each value of $K_j$ for which the audit can stop, weighted by the probability of drawing that value of $K_j$. The stopping condition may provide relationships among the various quantities. To obtain the risk of the entire audit, one sums the risks of each round. 

In \Minerva, the stopping condition relates the weighted average of the risks to the weighted average of the stopping probabilities over all values of $K_j$ for which the audit stops, for a given round size. Separate relationships between risk and stopping probability are not available for individual values of $K_j$. If the next round size depends on $K_j$, expressions relating the risks are not available, and we are not able to obtain an expression bounding the sum of the risks across rounds. Thus we are not able to determine if \Minerva is an RLA in this case, or if it is vulnerable to the strongly round-choosing adversary \cite{usenix_minerva, arxiv_athena, alpha}. 

In \Providence, we choose a stopping condition that applies separately to the risk and stopping probabilities for each value of $K_j$, avoiding the problem of \Minerva, and allowing for optimal round size choices, which depend on the drawn sample. 
The \Providence audit is risk-limiting even if a strongly round-choosing adversarial auditor determines round sizes after drawing the sample, and next round size computations may use knowledge of the current sample. 

\subsection{Definition}
\label{sec:prov_def}
\begin{definition}[$(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence]
    \label{def:minervatwo}
    For cumulative round size $n_j$ for round $j$ and a cumulative $k_j$ ballots for the reported winner found in round $j$, where samples are drawn with replacement, the \R \Providence stopping rule for the $j^{th}$ round is:
$$
\mathcal{A}(X_{j})=  \left\{ \begin{array}{ll} \text{Correct} ~~~~ \omega_{j}(k_{j}, k_{j-1}, p_a, p_0, n_j, n_{j-1}) \geq \frac{1}{\alpha}\\
        % & \\
        % incorrect& ~~~ \sigma_n < \frac{\beta}{1-\alpha} \\
        % & \\
        Undetermined ~~else \\
    \end{array}
    \right .
$$
where $\omega _{1}\triangleq \tau_{1}$ and for $j\ge 2$, we define $\omega _{j}$ as follows:
\begin{equation}
    \begin{aligned}
    \omega_{j}(k_{j}, k_{j-1}, p_a, p_0, n_{j}, n_{j-1})
    \triangleq\\
    \sigma(k_{j-1},p_a,p_0,n_{j-1})\cdot \tau_1(k_{j}-k_{j-1},p_a,p_0,n_j-n_{j-1})
    \end{aligned}
\end{equation}
\end{definition}

Notice that \Providence requires the computation of $\tau_j$ for $j=1$ and no other values of $j$. The value of $\tau_1$ is simply the ratio of the the tails of the binomial distributions (the distributions are binomial because the sampling is with replacement) for the two hypotheses and can be fairly efficiently computed. The computation of $\tau_j$ for $j \geq 2$, as required in \Minerva, relies on the convolution of two probability distribution functions and is hence computationally considerably more expensive. Smaller computational complexity makes audit planning and analysis using simulations as in section~\ref{sec:workload} more feasible.

Notice also that \Providence and \Minerva are identical for $j=1$. 

\subsection{Risk-Limiting Property: Proof}
\label{sec:proof}
We now prove that \Providence is risk-limiting against a strongly round-choosing adversary using lemmas from basic algebra which are given in Appendix~\ref{sec:proofs}.

\begin{theorem}
\label{thm:minerva2_is_rla_new}
$(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence is an
$\alpha$-RLA in the presence of a strongly round-choosing adversary.
\end{theorem}
\begin{proof}
Let $\mathcal{A}=(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence.
Let $\bm{n_j}$ be the cumulative round sizes used in this
audit, with corresponding cumulative tallies of
ballots for the reported winner $\bm{k_j}$.
For round $j=1$, by Definitions \ref{def:minervatwo}
and \ref{def:minerva_ratio}, we see that
the $\mathcal{A}=\text{Correct}$ (the audit stops) only when
$$
\tau_1(k_{1},p_a,p_0,n_1)\\
=\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge \frac{1}{\alpha}.
$$
By Lemma \ref{lemma:minerva2_kmin_exists} and Definition \ref{def:kmin}, there is 
a value $k_{min,1} = k^{p_a, p_0, \alpha, 0}_{min, 1, 0, n_1}$ such that 
$$
\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge
\frac{Pr[K_{1} \geq k_{min,1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{min, 1} \mid H_0, n_1]}
\ge 
\frac{1}{\alpha}.
$$

For any round $j\ge 2$, by Definition \ref{def:minervatwo}
and Lemma \ref{lemma:minerva2_kmin_exists},
$\mathcal{A}=\text{Correct}$ (the audit stops) if and only if
\begin{equation*}
\begin{aligned}
\omega_{j}(k_{j}, k_{j-1}, p_a, p_0, n_{j}, n_{j-1}, \alpha )\triangleq\\
\sigma(k_{j-1},p_a,p_0,n_{j-1})\cdot \tau_1(k_{j}-k_{j-1},p_a,p_0,n_j-n_{j-1})
\ge \frac{1}{\alpha}.
\end{aligned}
\end{equation*}
%Let $d_j=k_j-k_{j-1}$ be shorthand for the new draw.
%could do this for simpler notation^
By Lemma \ref{lemma:any_ratio_is_sigma_simple}
and Definition \ref{def:minerva_ratio}, this is equivalent to
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}
$$$$\ge \frac{1}{\alpha}.
$$
By Lemma~\ref{lemma:minerva2_kmin_exists} and Definition~\ref{def:minervatwo},
we see that there exists a $k_{min, j} = k^{p_a, p_0, \alpha, k_{j-1}}_{min, j, n_{j-1}, n_j}  \leq k_j$ 
%$k_{min, j}\le k_j$ 
for which
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]}\ge
$$
$$
\frac{\Pr[K_{j-1} = {k_{j-1}} \mid H_a, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_a, n_{j-1}, n_{j}]}{\Pr[K_{j-1} = {k_{j-1}} \mid H_0, n_{j-1}] Pr[K_{j} \ge k_{min, j} \mid {k_{j-1}}, H_0, n_{j-1}, n_{j}]} 
$$$$
\ge 
\frac{1}{\alpha}
$$
%Equivalently,
%$$
%\frac{Pr[K_{j} \ge k_{min, j}\wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_a]}{Pr[K_{j}\ge k_{min, j} \wedge K_{j-1} = k_{j-1} \mid n_{j}^*, k_{j-2}^*, H_0]}\ge \frac{1}{\alpha}.
%$$
%Taking the sum over all possible rounds and corresponding preceding values
%of $k$, we get
% Taking the sum over all possible audit histories, we get
The above may be rewritten as
\begin{equation*}
\begin{aligned}
\sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_0, n_{j-1}, n_{j}] \leq \\
\alpha \sum_{{k} = k_{min, j}}^{n_j} Pr[(K_{j} , K_{j-1}) = (k, k_{j-1}) \mid H_a, n_{j-1}, n_{j}]
\end{aligned}
\end{equation*}
The left hand side above is the probability of stopping in the $j^{th}$ round and $K_{j-1} = k_{j-1}$, given the null hypothesis, which is smaller than $\alpha$ times the same probability given the alternate hypothesis. 
For different possible values of $k_{j-1}$, different round sizes $n_j$ can be used, and this same relationship will hold. 
That is, the relationship\footnote{\Minerva enforces a similar relationship between risk and stopping probability but does so at the level of the round rather than for each individual value of $K_{j-1}$. By enforcing this relationship for each value of $K_{j-1}$, \Providence is resistant to a strongly round-choosing adversary.} holds even if the values of $n_{j}$ depend on $k_{j-1}$, if $n_j$ is a function $n_j(\alpha, p_0, p_1, ballot\_manifest, \bm{k_{j-1}}, \bm{n_{j-1}})$.

Summing both sides over all values of $k_{j-1} < k_{min, j-1}$ gives us a similar relationship between the probabilities of stopping in round $j$ (given the null and alternate hypotheses respectively)\footnote{In fact, this is the relationship \Minerva enforces for its stopping condition, additionally requiring that $n_j$ be fixed for all values of $k_{j-1}$.}. 
When both sides of the inequality are further summed over all rounds, we get:  

$$
Pr[\mathcal{A}=\text{Correct} \mid H_0]
\le
\alpha Pr[\mathcal{A}=\text{Correct} \mid H_a]
$$
Finally, because the total probability of stopping the audit under
the alternative hypothesis is not greater than 1, we get
$$
Pr[\mathcal{A}=\text{Correct} \mid H_0] \le
\alpha.
$$
\end{proof}

\subsection{Consequences of resistance to an adversary choosing round size}
\label{sec:adversary}
\input{sections/adversary}
